\documentclass[12pt]{amsart}
\input{preamble}
\setlength{\emergencystretch}{2pt}
\newtheoremstyle{case}{}{}{}{}{}{:}{ }{}
\theoremstyle{case}
\newtheorem{case}{Case}

\begin{document}
\title{Band-diagonal $M$-bases and\\
the $k$ point density property}
\author{Alexey Pyshkin}
%\begin{abstract}
  %%In the early 1990s the works of Larson, Wogen and Argyros, Lambrou, Longstaff
    %%disclosed an example of a strong tridiagonal $M$-basis that was not rank one dense.
  %%Later Katavolos, Lambrou and Papadakis studied $k$ point density property of this example.
  %%In this paper we present new methods for the analysis of $k$ point density
    %%and rank one density properties for band-diagonal $M$-bases.
%\end{abstract}
\keywords{biorthogonal system, $M$-basis, rank one density, two point density}
%\thanks{The author was supported by RFBR (the project~16-01-00674) and by «Native towns», a social investment program of PJSC «Gazprom Neft».}
\maketitle

\section{Introduction}
  \subsection{Density properties}
    Consider an infinite-dimensional Hilbert space $\cal{H}$.
    Suppose that $\cal{H}$ has an orthonormal basis $\{e_j\}_{j=0}^\infty$.
    A sequence $\fsys=\seq{f}$ of vectors in $\cal{H}$ is called \emph{minimal} if none of its elements can be approximated by the linear combinations of the others: $f_n \notin
      \overline{span}\big(\{f_k\}_{k \ne n}\big)$ for any $n$, where $\overline{span}$ denotes the closed linear span.
    The sequence $\fsys$ is said to be \emph{complete} when it spans the whole space $\overline{span}\big(\{f_k\}\big)=\cal{H}$.
    The system $\fstarsys = \{f_l^*\}_{l=0}^\infty$ is \emph{biorthogonal} if for any $k,l \geq 0$ we have $\inner{f_k}{f^*_l} = \delta_{kl}$, where $\delta$ is the Kronecker delta.
    It is known that $\fsys$ is complete and minimal when and only when it possesses a unique biorthogonal system $\fstarsys$.
    We call the minimal system $\fsys$ \emph{band-diagonal} if there exists $L \in \mathbb{N}$ such that $\inner{f_t}{e_l} = \inner{f^*_t}{e_l} = 0$
      whenever $\lvert t - l \rvert > L$.
    We say that $\fsys$ is an $M$-basis if $\fsys$ is complete and $\fstarsys$ is complete as well.
    Consider the operator algebra 
    \[
      \cal{A} = \{T\in B(\cal{H}): Tf_n = \lambda_n f_n, \text{ for some } \lambda_n \in \mathbb{R}, n \geq 0\},
    \]
      and the algebra $R_1(\cal{A})$ generated by rank one operators of $\cal{A}$.

    We are interested in the following density properties of these algebras.
    \begin{definition}[$k$ point density property]
      \label{kpd}
      We say that the algebra $\cal{A}$ has \emph{$k$ point density property} if for any $x_1, x_2,\dots x_k \in \cal{H}$ and $\varepsilon > 0$
        there exists $R\in R_1(\cal{A})$ such that $||Rx_s - x_s|| < \varepsilon$ for any $1 \leq s \leq k$.
    \end{definition}
    The definition for $k=1$ is equivalent to $\fsys$ being a \emph{strong $M$-basis} (see~\cite{katavolos}):
      the system $\fsys$ is called a \emph{strong $M$-basis} if for any $x\in\cal{H}$ we have $x \in \overline{span}\Big(\big\{\inner{x}{f^*_n}f_n\big\}_{n=0}^\infty\Big)$.
    \begin{definition}[rank one density property]
      \label{r1d}
      We say that the algebra $\cal{A}$ has \emph{rank one density property} if the unit ball of rank one subalgebra $R_1(\cal{A})$
        is dense in the unit ball of $\cal{A}$ in the strong operator topology.
    \end{definition}
    We say that $\fsys$ is $k$ point dense (rank one dense) when
      the corresponding algebra $R_1(\cal{A})$ is $k$ point dense (rank one dense).

    Notice that rank one density property implies $k$ point density property for any $k$.

  %\subsection{Motivation}
    %Long\-staff in~\cite{longstaff} studied abstract subspace lattices and corresponding operator algebras.
    %In that paper Longstaff raised an important question: does one point density property always imply rank one density property?

    %The solution remained unknown until Larson and Wogen showed~\cite{larson} that the answer is negative.
    %They constructed an example of a vector system $\fsys$ such that it is one point dense but does not possess rank one density property.
    %\begin{example}[Larson--Wogen system $\fsys_{LW}$ parameterized with real $a_n$]
      %\label{lw-sys}
      %For any $j \geq 0$ we define
      %\begin{align*}
        %&f_{2j+1}=-a_{2j+1}e_{2j} + e_{2j+1} + a_{2j+2}e_{2j+2} \qquad &f_{2j}=e_{2j},\\
        %&f^*_{2j}=-a_{2j}e_{2j-1} + e_{2j} + a_{2j+1}e_{2j+1} \qquad &f^*_{2j+1}=e_{2j+1},
      %\end{align*}
      %where $a_n$ are nonzero real numbers for any $n > 0$ and $a_0 = 0$.
    %\end{example}
    %The construction presented by Larson and Wogen was remarkably simple and elementary,~--- notice that the matrices corresponding to
      %the vectors $\{f_j\}_{j=0}^\infty$ and $\{f^*_j\}_{j=0}^\infty$ are both tridiagonal.
    %Afterwards this example was also studied in~\cite{argyroslambrou} (see Addendum), by Azoff and Shehada in~\cite{azoff}, in~\cite{me1}.
    %In 1993 Katavolos, Lambrou and Papadakis in~\cite{katavolos} performed a deep analysis of the density properties
      %of this vector system and deduced that for $\fsys_{LW}$ one point density does not imply rank one density.
    %Moreover, they showed that for such system rank one density is equivalent to two point density.

    %We are going to consider band-diagonal systems similar to the one regarded by Larson and Wogen and to determine the exact conditions
      %for $k$ point density property of such vector systems.
    %In this paper we present a few new techniques for the analysis of $k$ point density and rank one density of band-diagonal vector systems.

\section{Chain of reflexive closures for B-class}
  In this section we denote the rank one operator subalgebra $R_1(\cal{A})$ with $R$.
  %\label{sec:preliminaries}
  \begin{definition}
    Let $U$ be a linear subspace of operators.
    Then $ref_k(U) = (F_k \cap R_\perp)^{\perp}$ is called \emph{$k$-reflexive closure} of $U$.
    Here $F_k$ is a linear subspace of all rank $k$ operators, $U_\perp$ means the preannihilator of $U$ and
      $U^\perp$ denotes the annihilator of $U$ (both with respect to the weak star topology induced by trace).
  \end{definition}
  It is well-known that $ref_{k + 1}(U) \subseteq ref_k(U)$ for any linear subspace $U$.

  We will denote the weak star closure of $R$ with $w_0(R)$ and the weak star closure of $R$ and the identity operator with $w(R)$.
  Moreover for any linear subspace $U$ there is a chain of inclusions
  \[
    ref_1(U) \supseteq ref_2(U) \supseteq \dots \supseteq ref_k(U) \supseteq \dots \supseteq w_0(U),
  \]
  In their paper \cite{azoff2} of 1993 Azoff and Shehada suggested such algebra $U$, generated by
    mutually orthogonal idempotents that only one of inclusions was strict:
  \[
    ref_1(U) = \dots = ref_k(U) \supsetneq ref_{k + 1}(U) = ref_{k+2}(U) = \dots = w_0(U),
  \]
    for any given $k > 0$.
  Also they provided an example where all the inclusions were strict.
  This way it was shown that this chain of inclusions can be very different for various $U$.
  The main idea of that paper is tightly connected to the technique in the famous paper of Wogen~\cite{wogen}
    exploiting the properties of the shift operator.

  For us the first important thing is that the idempotents in their construction were not necessarily rank one operators.
  The second thing is that in their construction the identity operator did not belong even to $ref_1(U)$.
  Indeed, the rank one density property is the same as $I \in w_0(R)$,
    while the $k$ point density property is equivalent to having $I$ in $ref_k(R)$.

  Suppose that $\fsys=\{f_n\}_{n=0}^\infty$ is an arbitrary B-class $M$-basis and
    $\fstarsys = \{f^*_n\}_{n=0}^\infty$ is its biorthogonal sequence.
  Again, we consider the operator algebra $\cal{A} = \{T\in B(\cal{H}): Tf_n = \lambda_n f_n,
    \text{ for some } \lambda_n \in \mathbb{R}, n \geq 0\}$
    and the algebra $R(\cal{A})$ generated by rank one operators of $\cal{A}$.


  The next theorem shows that for B-class the chain of inclusions always contains
    exactly one strict inclusion.
  \begin{theorem}
    \label{thm:chain}
    Then $I \in ref_k(R)$ but $I \not\in ref_{k+1}(R)$ if and only if $R$ is $k + 1$-reflexive but not $k$-reflexive, moreover,
      the following holds:
    \[
      \cal{A} = ref_1(R) = ref_2(R) = \dots = ref_k(R) \supsetneq ref_{k + 1}(R) = \dots = w_0(R).
    \]
  \end{theorem}
  The proof follows from the next proposition which
   is a generalization of Theorem 5.2 of Azoff and Shehada in their paper~\cite{azoff}.
  \begin{prop}
    $w(R)$ is 1-reflexive.
  \end{prop}
  \begin{proof}
    Let $s_n = \sum_{k=1}^n f^*_k \otimes f_k$ and $p_n = \sum_{k=1}^n e_k \otimes e_k$.
    \begin{lemma}
      We have
      \begin{align*}
        &s_m p_n = p_n s_m = s_m, \qquad n > m + D,\\
        &s_m p_n = p_n s_m = p_n, \qquad n < m - D,
      \end{align*}
      where $D$ is the width of $\fsys$.
    \end{lemma}
    \begin{proof}
      Let $E_\Delta = span(\{e_k\}_{k=n-D}^{n+D})$.
      The width of the system is $D$ and so $Ran(s_m - p_m) \subseteq E_\Delta$.
      It can be also seen that $Ker(s_m - p_m) \subseteq E_\Delta$.
      The lemma follows.
    \end{proof}
    Suppose we have an operator $t \in w(R)_\perp$.
    It implies that the trace of $t$ is zero.
    We define a finite rank approximations of $t$
    \[
      t_n = p_n t p_n - \sum_{l = n - D}^{n + D + 1} \alpha_{nl} e_l \otimes e_l,
    \]
    where $\alpha_{nl} = tr(p_n s_l p_n t) - \displaystyle\sum_{s = n-D}^{l - 1} \alpha_{n s}$.
    \begin{lemma}
      The sequence $t_n$ tends to $t$ in SOT.
    \end{lemma}
    \begin{proof}
      The first member $p_n t p_n$ tends to $t$ in SOT, and the sum of $\alpha_{nl}$ equals to 
        $tr(t p_n)$ and tends to zero, since $tr(t) = 0$.
    \end{proof}
    \begin{lemma}
      Each $t_n$ belongs to $w(R)_\perp$.
    \end{lemma}
    \begin{proof}
      The values of $\alpha_{nl}$ are chosen specifically for this lemma to hold.
    \end{proof}
    The most interesting part of the proof is the following lemma, where we appeal to the algebraic properties
      of the preannihilator.
    \begin{lemma}
     $t_n$ belongs to a span of rank one operators from $w(R)_\perp$.
    \end{lemma}
    \begin{proof}
      Notice that $t_n = t_n p_{n + D + 1} = t_n p_{n + D + 1} s_n = t_n s_n.$
      Since the $w(R)_\perp$ is closed under multiplication on the elements of the algebra $\cal{A}$,
        each rank one summand of $t_n s_n$ belongs to the preannihilator.
    \end{proof}
    The last lemma finishes the proof of the proposition.
  \end{proof}

  \begin{proof}[Proof of Theorem~\ref{thm:chain}]
    We choose the minimal $k$ such that $I \not\in ref_k(R)$.
    If there is no such $k$ then the fact follows from the proposition right away.
    It means that there is an operator $t_k \in ref_k(R)$ such that $tr(t_k) \neq 0$.
    Then any operator $t$ from $w_0(T)$ can be approximated with $t_k$ and $ref_k(R) \cap I_\perp$,
      since $t$ can be seen as a sum $\beta t_k + (t - \beta t_k)$, where $\beta$ is equal to $tr(t)/ tr(t_k)$.
    It follows that $ref_s(R) = ref_{s+1}(R)$ for any $s \geq k$, or that $w_0(R)$ is $k$-reflexive.
    If $k$ is zero then the proof is finished.
    Otherwise $I \not\in ref_k(R)$ and $I \in ref_{k - 1}(R)$, and this is the spot where we have
      the strict inclusion.
    For all $s < k$ we have $ref_s(R) = ref_{s-1}(R)$ due to the fact that
    \[
      ref_s(R) = (R_\perp \cap F_s)^\perp = ref_s(w(R)) = ref_{s - 1}(w(R)) = ref_{s-1}(R).
    \]
  \end{proof}

\section{Rank one density and two point density}
  The setup is the same as in the previous section.
  \begin{theorem}
    The system $\fsys$ is rank one dense if and only if it is two point dense.
  \end{theorem}
  \begin{proof}
    We start with the key proposition.
    \begin{prop}
      The operator algebra $\cal{A}$ has a separation vector.
    \end{prop}
    \begin{proof}
      The algebra $\cal{A}$ contains bounded operators with $f_n$ as eigenvectors.
      Consider $x = \sum \gamma_n f_n$, where $\gamma_n = n^{-1}\|f_n\|^{-1}$.
      The vector $x$ belongs to $\cal{H}$ since the series converges absolutely.

      Suppose there is an operator $a \in \cal{A}$ such that $ax = 0$.
      Since $a$ belongs to $\cal{A}$ there are some $\beta_n$ such that
      $a f_n = \beta_n f_n$.
      Obviously $\beta_n$ are bounded by the norm of the operator $a$.

      Now, $ax = \sum \gamma_n a f_n$, since the series converges absolutely.
      We also can see that $a f_n = \beta_n f_n$ and so $ax = \sum \gamma_n \beta_n f_n$,
        and the series converges absolutely again.
      Since $ax = 0$, we conclude that $\inner{ax}{f^*_n} = \gamma_n \beta_n = 0$ for any $n$.
      It follows that $\beta_n = 0$ for $n$, and so $a = 0$.
    \end{proof}

    It follows that the weak star closure of rank one operators $w_0(R) \subseteq \cal{A}$ also has a separation vector.
    The following proposition is a known fact, but we provide a proof for the sake of completeness.
    \begin{prop}
      $S$ is a norm closed linear subset of $B(H)$ and there is a separation vector $x$ for $S$.
      Then $S$ is 2-reflexive.
    \end{prop}
    \begin{proof}
      Suppose $t \in ref_2(S)$.
      It implies that for any vector $y \in \cal{H}$, there is an operator $s_y \in S$ such that
        $tx = s_y(x)$ and $ty = s_y(y)$.
      The vector $x$ is a separation vector for $S$, so there can be only one such $s_y \in S$.
      Thus $s_y$ does not really depend on $y$ and $t$ is equal to $s_y$, which means that $t$ belongs
        to $S$.
    \end{proof}
    Combining these two propositions we get that $w_0(R)$ is two reflexive.
    It means that $ref_2(R) = w_0(R)$ and rank one density is equivalent to two point density for $\fsys$.
  \end{proof}

\section{B-class: reordered basis view}
  \subsection{General points and Larson-Wogen system}
    [In this section the notation of ONB $\{e_n\}$ is being a little abused, but is easy to deduce from the context.]

    \medskip
    It is conceivable that $\fsys$ is equal to $e_n$ for any even $n$.
    The same can be said about $\fstarsys$ (only $n$ must be odd)
    The idea is to regroup this two parts of ONB and see what happens.

    So lets look at the linear map $\Phi$ that performs the transition between ${e_n}$ and ${f_n}$.
    It is easy to see that it is a two-by-two block matrix:
    \[
      \Phi= \left( {
        \begin{array}{cc}
          I & A\\
          0 & I\\
        \end{array}
      }
    \right).
    \]
    For instance for Larson-Wogen example the matrix $A$ is a two-diagonal matrix:
    \[
      A = \sum a_k e_k \otimes e_k + a_{k + 1} e_{k + 1} \otimes e_k.
    \]
    For the ladder example (TODO define) the matrix $A$ is a tridiagonal matrix.

    The biorthogonal system $\fstarsys$ corresponds to a very similar matrix
    \[
      \Phi_* = \left( {
        \begin{array}{cc}
           I   & 0\\
          -A^* & I\\
        \end{array}
        }
      \right).
    \]
    Just to remind: B-class system is always an $M$-basis.

    Let us reformulate the rank one density problem for the case when $A$ is a bounded operator on a Hilbert space.
    The rank one density of $\fsys$ means that for any trace class operator $t$ which belongs to $R_\perp$,
      we have $tr(t) = 0$.

    Look at the operator $t$ as a two-by-two matrix
    \[
      t = \left({
            \begin{array}{cc}
              t_{11} &t_{12}\\
              t_{21} &t_{22}\\
            \end{array}
            }
          \right).
    \]
    The condition $t \in R_\perp$ can be rewritten as $ \inner{t\Phi e_n}{\Phi_* e_n} = 0$.
    That is the same as $\inner{t_{\Phi}e_n}{e_n} = 0$, where $t_{\Phi} = (\Phi_*)^* t \Phi = \Phi^{-1} t \Phi$.
    When $A$ is bounded then this is always true.
    We are interested in the diagonal elements of $t_\Phi$ while $t_\Phi$ can be viewed as the following two-by-two matrix:
    \[
      t_\Phi = \left({
               \begin{array}{cc}
                 t_{11} + At_{21} & *\\
                 * & -t_{21}A + t_{22}\\
               \end{array}
             }
             \right).
    \]
    It follows that $\sum_n \inner{(t_{11} + At_{21}) e_n}{e_n} + \sum_n \inner{(-t_{21}A + t_{22})e_n}{e_n} = 0$.
    Notice that for the case of bounded operator $A$ we have
    \begin{align*}
      tr(t_{11}) + tr(t_{22}) = \sum_n \inner{t_{21}A e_n}{e_n} - \sum_n \inner{At_{21} e_n}{e_n} =\\
        tr(t_{21}A) - tr(At_{21}) = 0.
    \end{align*}
    This way we proved that for B-class when the symbol $A$ is a bounded operator then the rank one density holds.

    The question is whether we can build some unbounded $A$ such that the operator $t$ belongs to the trace class
      but not in $F_k$.

    The "easier" question is whether we can build some unbounded $A$ such that operator $t_{21}$ belongs to the trace class
      but not in $F_k$ and $\sum_{\text{diag}}At_{21} \neq \sum_{\text{diag}}t_{21}A$.

    For example for the diagonal operator $A = \sum_k \lambda_k e_k \otimes e_k$ where $\lambda_k$ are not necessarily bounded
      we always have $tr(At_{21}) = tr(t_{21}A)$,
      and also the system $\fsys_A$ is always rank one dense.

    For the two-diagonal operator $A = \sum_k \lambda_k e_k \otimes e_k + \mu_k e_{k + 1} \otimes e_k$ (Larson-Wogen) we get that
    \begin{align*}
      \sum_{\text{diag}} At = \sum_n (\mu_{n-1} t_{n-1 n} + \lambda_n t_{nn}),\\
      \sum_{\text{diag}} tA = \sum_n (\mu_n t_{n n+1} + \lambda_n t_{nn}).
    \end{align*}
    We can view this is as follows:
      in the case of $At$ we have the sum of the rows of the some infinite table and in the case of
      $tA$ the sum is over the columns of the same table ($t_{ij}$ being multiplied to the same coefficients in both cases).
    It is rather straightforward in this example to build such $A$ and $t$ that both sums are finite but not equal.
  \subsection{Retrospective of pentadiagonal example}
    In~\cite{me2} we constructed a pentadiagonal example very similar to Larson-Wogen system though
      it had the same density properties as LW-system.

    It is interesting that the system is not in the B-class however it can be inscribed in a more
      general context using the ideas of previous section.

    Namely, lets look at the matrix $\Phi$ of the subsystem in~\cite{me2}.
    Notice that it is a three-by-three matrix and looks like
    \[
      \Phi = \left( {
        \begin{array}{ccc}
           I & A & B\\
           0 & I & C\\
           0 & 0 & I\\
        \end{array}
        }
      \right),
    \]
    where $B = AC$ is the necessary condition for the minimality of the system.
    So in a way this system is not generated by a bipartite graph but rather by a three-partite graph.

    In the example of~\cite{me2} the matrices $A$ and $B$ are 2-diagonal and $C$ is 1-diagonal.

  \subsection{A reformulation for $k$-point density}
  Suppose that the matrix $A$ is real-valued.
  Denote with $A_*$ the formal conjugate matrix to $A$.
  \begin{prop}
    The system $\fsys$ is one point dense if and only if $\operatorname{Ker}(id - A_* A) = \varnothing$.
  \end{prop}
  \begin{prop}
    The system $\fsys$ is two point dense if and only if for any $x, u, v, y \in \ell^2(\mathrm{C})$
    and some real-valued sequences $\seq{\lambda}, \seq{\mu}$ such that
    \begin{align*}
      Au=-v + \lambda \odot x,\\
      A_*x = y + \mu \odot u,
    \end{align*}
    it is true that $\operatorname{Im}(v \bar{x} + u \bar{y}) = 0$.
  \end{prop}
  %\begin{corol}
    %If $\fsys$ is not two point dense, then there exist $x, u, v, y \in \ell^2(\mathrm{C})$
    %and real-valued sequences $\seq{\lambda}, \seq{\mu}$ such that

  %\end{corol}

\section{Ladder vector system investigation: the rank one density is equivalent to the two point density}
  TODO

  %Now consider an operator $T$ which has a finite rank.
  %In this case we write $T$ as a finite sum $T = \sum_{s=1}^k y^s \otimes x^s$,
    %where $x^s, y^s \in \cal{H}$ and $y \otimes x$ denotes the rank one operator sending a vector $v \in \cal{H}$
    %to $\inner{v}{y}x$.

  %Let us define vectors $v_n$ and $u_n$ in $\mathbb{R}^k$ as follows:
  %\begin{equation*}
    %v_n = (x^1_n, x^2_n, \dots, x^k_n)\qquad
    %u_n = (y^1_n, y^2_n, \dots, y^k_n),
  %\end{equation*}
  %where $x^s_n = \inner{x^s}{e_n}$ and $y^s_n = \inner{y^s}{e_n}$.
  %Since $\inner{Te_m}{e_l} = \inner{u_m}{v_l}$ for any $m$ and $l$, we can rewrite $\Xi_n$ in terms of
    %the scalar products of $\{u_n\}_{n=0}^\infty$ and $\{v_n\}_{n=0}^\infty$.
  %In turn it means that~\eqref{eq:prop:ref} can be rewritten in terms of the scalar products
    %of $\{u_n\}_{n=0}^\infty$ and $\{v_n\}_{n=0}^\infty$.

  %Hence, the existence of $T$ would be reduced to the existence of
    %the vectors $u_n$, $v_n$ in $\mathbb{R}^k$ such that the sequences $\{\lvert u_n\rvert\}_{n=0}^\infty$,
    %$\{\lvert v_n\rvert\}_{n=0}^\infty$ are both square summable and~\eqref{eq:prop:ref} is satisfied.
  %Thus, instead of looking for $k$ vectors $x^s$ and $y^s$ in $\cal{H}$, we would look for an infinite sequence
    %of $k$-dimensional vectors $v_n$ and $u_n$ such that $\{v_n \}_{n=0}^\infty$, $\{u_n\}_{n=0}^\infty$ belong to $\ell^2(\mathbb{R}^k)$.
  %This is one of the key ideas in our method of analysing $k$ point density property for $\fsys$.

  %Thus, we have just found the following reformulation for $k$ point density property.
  %\begin{prop}
    %\label{prop:kreformulation}
    %The following two statements are equivalent:
    %\begin{enumerate}
      %\item there exists a $k$-dimensional operator $T$ which annihilates $R_1(\cal{A})$
        %such that $Tr\, T \neq 0$,
      %\item there exist vectors $\{u_n\}_{n=0}^\infty$, $\{v_n\}_{n=0}^\infty$ in $\ell^2(\mathbb{R}^k)$ such that
        %for the operator $\widehat{T} = \displaystyle\sum_{t,l=0}^\infty \inner{u_t}{v_l} e_t \otimes e_l$ we have
        %\begin{equation}
          %\label{eq:thm}
          %\Xi_n + \sum_{m=0}^n \inner{\widehat{T}e_m}{e_m} = 0
        %\end{equation}
          %for any $n \geq 0$.
    %\end{enumerate}
  %\end{prop}
  %As we already mentioned, the equation~\eqref{eq:thm} can be expressed via $u_n$ and $v_n$.
  %Moreover, we can also write the trace of $T$ in terms of $u_n$, $v_n$:
  %%\begin{prop*}
    %\begin{equation}
      %\label{eq:propstar}
      %%\begin{align*}
        %Tr\,T = \sum_{s=1}^k \langle y^s, x^s \rangle = \sum_{s=1}^k \sum_{n=0}^\infty y^s_n x^s_n
              %= \sum_{n=0}^\infty \sum_{s=1}^k y^s_n x^s_n = \sum_{n=0}^\infty \langle u_n, v_n \rangle.
      %%\end{align*}
    %\end{equation}
  %%\end{prop*}
  %Essentially, the $k$ point density property can be viewed as a
    %possibility of placing the sequence of vectors in $\mathbb{R}^k$ which are constrained with
    %a series of relations~\eqref{eq:thm} and~\eqref{eq:propstar}.
%\input{lw-classification}
%\input{pentadiagonal-classification}
%\bigskip

%\section{Acknowledgements}
  %This is part of author's Ph.D. thesis, written under the supervision of Anton Baranov at the PDMI RAS.
  %The author gratefully acknowledges the many helpful suggestions of Anton Baranov during the preparation of the paper.

\input{bib}
\end{document}
