\documentclass[12pt]{amsart}
\input{preamble}
\newtheoremstyle{case}{}{}{}{}{}{:}{ }{}
\theoremstyle{case}
\newtheorem{case}{Case}

\begin{document}
\title{On rank one density problem for one pentadiagonal $M$-basis}
\author{Alexey Pyshkin}
\maketitle

\section{Introduction}
\section{Preliminaries}
  We will discuss some properties of a particular system of vectors in a separable Hilbert space $\cal{H}$.
  We assume that $\cal{H}$ is a real Hilbert space. 
  Suppose that $\cal{H}$ has an orthonormal basis $\{e_j\}_{j=1}^\infty$.
  We are exploring a complete and minimal system $\{f_n\}$ and its biorthogonal system $\{f^*_n\}$ defined as follows:
  \begin{equation}
    \label{main-system}
    \begin{aligned}
      &\mathbf{f_{4j}} = e_{4j} \quad 
      \mathbf{f^*_{4j}} = e_{4j} + d_{2j - 1} e_{4j-2} - b_{2j-1} e_{4j-1} + a_{2j} e_{4j+1} + c_{2j} e_{4j+2} \qquad
      (j > 0),\\
      &\mathbf{f_{4j+1}} = -a_{2j} e_{4j} + e_{4j+1} \quad 
      \mathbf{f^*_{4j+1}} = e_{4j+1} + b_{2j} e_{4j+2},\\
      &\mathbf{f_{4j+2}} = e_{4j+2} + d_{2j} e_{4j} - b_{2j} e_{4j+1} + a_{2j+1} e_{4j+3} + c_{2j+1} e_{4j+4}\quad
      \mathbf{f^*_{4j+2}} = e_{4j+2},\\
      &\mathbf{f_{4j+3}} = e_{4j+3} + b_{2j+1} e_{4j+4}\quad
      \mathbf{f^*_{4j+3}} = -a_{2j+1} e_{4j+2} + e_{4j+3},
    \end{aligned}
  \end{equation}
    where the coefficients $a_n$, $b_n$, $c_n$, $d_n$ are equal to zero whenever $n$ is less than one, and are bound with the equality
    $c_n + d_n = a_n b_n$. 
  \begin{prop}
    The given system is an $M$-basis if the coefficients satisfy the restrictions above.
  \end{prop}
  \begin{proof}
    The equality $c_n + d_n = a_n b_n$ guarantees the bi\-orthogonality,
    while the completeness of the $\{f_n\}$ and $\{f_n^*\}$ is
    easy to check.
  \end{proof}
  
  \begin{theorem}
      The given system is NOT $k$-complete for some (equivalently any) $k > 1$ iff the sequence
      $$
          \mu_n = \min(1/|a_n| + 1/|b_n|, (1 + |b_n|)/|d_n|, (1 + |a_n|)/|c_n|)
      $$ belongs to $l^1$.
  \end{theorem}
  \begin{proof}
      Let us consider a $k$-dimensional operator $T$ such that 
      $Tr(TR) = 0$ for each $R \in \cal{R}_1(\cal{A})$ which essentially means that
      $\langle Tf_n, f_n^* \rangle = 0$ for any $n > 0$. 
      Notice that the partial sums of the Fourier series for the given system are somehow close to the
      partial sums of the canonical Fourier series (using the orthonormal basis $e_n$). Define
      $$
        \Xi_n := \sum_1^n \langle Tf_s, f_s^* \rangle - \sum_1^n \langle Te_s, e_s \rangle = -\sum_1^n \langle Te_s, e_s \rangle.
      $$
      where the $\langle \cdot, \cdot\rangle$ denotes the inner product in $\cal{H}$.
      These residuals has also a concise form:
      \begin{align*}
          \Xi_{4j} = a_{2j} T_{4j+1, 4j} + c_{2j} T_{4j+2, 4j},\\
          \Xi_{4j + 1} = -d_{2j} T_{4j+2, 4j} + b_{2j} T_{4j+2, 4j+1},\\
          \Xi_{4j + 2} = a_{2j+1} T_{4j+2, 4j+3} + c_{2j+1} T_{4j+2, 4j+4},\\
          \Xi_{4j + 3} = -d_{2j+1} T_{4j+2, 4j+4} + b_{2j+1} T_{4j+3, 4j+4},
      \end{align*}
      having $T_{ij}$ equal to the $\langle Te_j, e_i\rangle$.
      \begin{prop}
          \label{inf-dim-statement}
          There exists an operator $T$ with trace equal to $-1$ such that
            $\langle Tf_n, f_n^*\rangle = 0$ for any $n$ if and only if the
            sequence from the statement of the theorem $\left\{\mu_n\right\}$ belong to $\ell^1$.
      \end{prop}
      \begin{proof}
          Assume that $\mu_n \in \ell^1$.
          We will then construct a required operator $T$.
          Let $T_{11}$ be equal to $-1$, and $T_{jj}$ be equal to zero for any other $j$.
          Then for each $n$ we have three cases.

          \noindent\textbf{Case 1.} Suppose $\mu_n = 1/|a_n| + 1/|b_n|$. For $n=2j$ we set:
          \begin{align*}
            T_{4j+1,4j}&=1/a_n & \quad T_{4j+2,4j} = 0,\\
            T_{4j+2,4j+1}&=1/b_n.
          \end{align*}
          That guarantees an equality $\Xi_{4j} = \Xi_{4j+1} = 1$.
          For $n=2j+1$ we set:
          \begin{align*}
            T_{4j+2,4j+3}&=1/a_n & \quad T_{4j+2,4j+4} = 0,\\
            T_{4j+3,4j+4}&=1/b_n,
          \end{align*}
          which provides an equality $\Xi_{4j+2} = \Xi_{4j+3} = 1$.

          \noindent\textbf{Case 2.} Assume $\mu_n = (1 + |b_n|)/|d_n|$. 
          For $n=2j$ we set
          \begin{align*}
            T_{4j+1,4j} &= b_{2j}/d_{2j} & \quad T_{4j+2,4j} = -1/d_{2j},\\
            T_{4j+2,4j+1} &= 0.
          \end{align*}
          The case $n = 2j + 1$ is left to the reader.

          \noindent\textbf{Case 3.} Suppose $\mu_n = (1 + |a_n|)/|c_n|$. 
          For $n = 2j + 1$ we assign:
          \begin{align*}
            T_{4j+2,4j+3} &= 0 & \quad T_{4j+2,4j+4} = 1/c_{2j+1},\\
            T_{4j+3,4j+4} &= a_{2j+1}/c_{2j+1}.
          \end{align*}
          The case $n = 2j$ is analogous.
          All the other entries $T_{ij}$ we set to zero.

          The constructed operator $T$ belongs to the trace class since all the non-zero elements are summable 
            dut to the assumption that $\left\{\mu_n\right\} \in \ell^1$.
          These assignments ensure that $\Xi_n = 1$ for any $n > 1$.
          Since the trace of the operator $T$ is equal to $-1$ and $T$ annihilates all the rank one operators $f^*_n \otimes f_n$,
            the sufficiency is proved.
          \medskip\\
          Now assume that there exists a trace class operator $T$ with all the properties we require.
          Then obviously all the $T_{nn}, T_{n, n+1}, T_{n, n+2}$ elements are summable (simple property of a trace class operator matrix).
          As we know $\Xi_n$ tends to $1$ since the trace of the operator is $-1$. Let us consider a sum
          $|T_{4j+1, 4j}| + |T_{4j+2,4j}| + |T_{4j+2,4j+1}|$. It depends linearly on $T_{4j+2, 4j}$ and the minimum
          is obtained on the boundary of the domain. The minimum value is greater than $\mu_{2j}/2$ whenever $j$ is
          sufficiently large.
          The second pair of equalities gives out the minimum value greater than $\mu_{2j+1}/2$ when $j$ is large,
          which shows that the stated condition is necessary for the existence of operator $T$.
      \end{proof}
      Now consider the case of the $k$-dimensional operator $T$.
      Let us put the operator $T$ as a sum of $k$ rank one operators:
      $$
          T = \sum_1^k y^s \otimes x^s,
      $$
      where $x^s, y^s \in \cal{H}$
      Therefore $T_{ij} = \sum {y^s_j x^s_i}$.
      Let us define vectors $v_n$ and $u_n$ which lie within $\mathbb{R}^k$ as follows:
      \begin{align*}
          v_{2j} &= (y^1_{4j}, y^2_{4j}, \dots ,y^k_{4j}) \quad
          &v^*_{2j} = (x^1_{4j}, x^2_{4j}, \dots ,x^k_{4j}) \\
          v_{2j+1} &= (x^1_{4j+2}, x^2_{4j+2}, \dots ,x^k_{4j+2}) \quad
          &v^*_{2j+1} = (y^1_{4j+2}, y^2_{4j+2}, \dots ,y^k_{4j+2}) \\
          u_{2j} &= (x^1_{4j+1}, x^2_{4j+1}, \dots ,x^k_{4j+1}) \quad
          &u^*_{2j} = (y^1_{4j+1}, y^2_{4j+1}, \dots ,y^k_{4j+1}) \\
          u_{2j+1} &= (y^1_{4j+3}, y^2_{4j+3}, \dots ,y^k_{4j+3}) \quad
          &u^*_{2j+1} = (x^1_{4j+3}, x^2_{4j+3}, \dots ,x^k_{4j+3}) 
      \end{align*}
      Note that the sequences $|v_n|$, $|u_n|$ belong to $l^2$. Also $u_n$ and $v_n$ are defined for all $n > 0$.
      We can rewrite the previous equations using the introduced vectors:
      \begin{align*}
          \Xi_{4j} &= a_{2j} \langle u_{2j}, v_{2j}\rangle + c_{2j} \langle v_{2j+1}, v_{2j}\rangle,\\
          \Xi_{4j + 1} &= -d_{2j} \langle v_{2j+1}, v_{2j}\rangle + b_{2j} \langle v_{2j+1}, u_{2j}\rangle,\\
          \Xi_{4j + 2} &= a_{2j+1} \langle v_{2j+1}, u_{2j+1} \rangle + c_{2j+1} \langle v_{2j+1}, v_{2j+2} \rangle,\\
          \Xi_{4j + 3} &= -d_{2j+1} \langle v_{2j+1}, v_{2j+2}\rangle + b_{2j+1} \langle u_{2j+1}, v_{2j+2} \rangle.
      \end{align*}
      Here the $\langle\cdot, \cdot\rangle$ denotes the scalar product in $\mathbb{R}^k$.
      \begin{note}
        Observe that in such setup we always have $\Xi_n = 0$ for any $n \leq 1$.
      \end{note}
      Since the vectors are in the $R^k$ we are able to reduce the system to
      \begin{align*}
        \Xi_{2j} &= a_{j} \langle u_{j}, v_{j} \rangle  + c_{j} \langle v_{j+1}, v_{j} \rangle,\\
        \Xi_{2j + 1} &= -d_{j} \langle v_{j+1}, v_{j} \rangle + b_{j} \langle v_{j+1}, u_{j}\rangle.
      \end{align*}
      We get that the existence of an operator $T$ might be reduced to the existence of vectors $u_n$, $v_n$ in the $\mathbb{R}^k$
        which respects the conditions given above.
      Given that the sequences of vectors $u_n$, $v_n$ lie in the $\mathbb{R}^k$ we might think of the scalar product as
        the usual product of the vector lengths and the cosinus of the angle between the vectors.
      \begin{prop}
          \label{k-dim-statement}
          If $\left\{\mu_n\right\}$ belongs to $l^1$ then it is possible to construct such vectors $u_n$ and $v_n$ that the equations above are true and for any $n > 1$ we have $\Xi_n = 1$.
      \end{prop}
      \begin{proof}
          The operator matrix is going to look very similar to one we built in the previous proposition.
          Again we are going to look at three possible values of the $\mu_n$.
          For each $n$ we are going to find $V_n = |v_n|$, $U_n = |u_n|$ and three angles:
          $\alpha_n$~--- is the angle between $v_n$ and $v_{n + 1}$, and
          $\beta_n$~--- is the angle between $v_n$ and $u_n$.
          $\gamma_n$~--- is the angle between $v_{n + 1}$ and $u_n$.
          Let $V_1$ be equal to one.
          We choose the $v^*_1$ vector such that $\langle v_1, v^*_1 \rangle = -1$ and set all
          the other $u^*_n$, $v^*_n$ to zero. That guarantees that the trace of the constructed operator (if it
          will fall within the trace class) is equal to $-1$.\\
          Within the construction we are going to set all the $V_n$ inductively. In order to do
          that we are going to define an auxiliary sequence $M_n \in l^2$ such that for any $n$ greater than zero
          $V_n \geq M_n$. On each step $n$ we are going to define $V_n$ and $M_{n+1}$.
          
          So let us start the construction with the setting $M_1 = 1$.\\
          \textbf{Case 1:} $\mu_n = 1/|a_n| + 1/|b_n|$\\
              Here we want to have $v_n$ orthogonal to $v_{n+1}$.
              Set
              \begin{align*}
                  V_n &:= \max\left(M_n, \frac{1}{\sqrt{\smash[b]{|a_n|}}}\right),\\
                  U_n &:= \left(\frac{1}{a_n^2 V_n^2} + \frac{1}{b_n^2 V_{n+1}^2}\right)^\frac{1}{2},\\
                  M_{n+1} &:= \frac{1}{\sqrt{\smash[b]{|b_n|}}}.
              \end{align*}
              \begin{prop}
                  The following inequalities are true:
                  \begin{align*}
                      M_{n+1} &\leq \sqrt{\mu_n},\\
                      U_n &\leq \sqrt{\mu_n},\\
                      V_n &\leq \max(\sqrt{\mu_n}, M_n).
                  \end{align*}
                  There exist such angles $\beta_n$, $\gamma_n$ that with the values $U_n$, $V_n$ defined like this the following is true:
                  \begin{align*}
                      \langle u_n, v_n \rangle &= 1/a_n,\\
                      \langle u_n, v_{n+1} \rangle &= 1/b_n,\\
                      \langle v_n, v_{n+1} \rangle &= 0.
                  \end{align*}
              \end{prop}
              \begin{proof}
                  First part of the proposition is a simple exercise.\\
                  Now we want to understand why there exist such $\beta_n$ and $\gamma_n$ that all the scalar products of
                  $v_n$, $v_{n+1}$, $u_n$ satisfy the conditions above.
                  Now observe that the chosen $U_n$, $1/(|a_n| V_n)$ and $1/(|b_n| V_{n+1})$ 
                  comprise a right triangle with $U_n$ as a hypotenuse.
                  As a result there always be such $\beta_n$ and $\gamma_n$ that
                  \begin{align*}
                      |U_n \cos{\beta_n}| &= \frac{1}{|a_n|V_n},\\
                      \left|U_n \cos{\gamma_n}\right| &= \left|U_n \sin{\beta_n}\right| = \frac{1}{|b_n|V_{n+1}}.
                  \end{align*}
              \end{proof}
          \noindent\textbf{Case 2:} $\mu_n = (1 + |a_n|)/|c_n|$\\
              Here we will have $u_n$ orthogonal to $v_n$.
              Assign:
              \begin{align*}
                  M_{n+1} &:= \max\biggl(\smash[b]{\frac{\sqrt{|a_n|}}{\sqrt{|c_n|}}}, \frac{1}{\sqrt{\smash[b]{|c_n|}}}\biggr),\\
                  V_n &:= \max\left(M_n, \frac{2}{\sqrt{\smash[b]{|c_n|}}}\right),\\
                  \alpha_n &:= \arccos{\frac{1}{c_n V_n V_{n+1}}},\\
                  \gamma_n &:= \frac{\pi}{2} \pm \alpha_n,\\
                  U_n &:= \frac{a_n}{c_n \cos{\gamma_n} V_{n+1}}.
              \end{align*}
              \begin{remark*}
                  We choose plus or minus in the expression of $\gamma_n$ in order to make the $a_n/(c_n \cos{\gamma_n})$ always positive.
              \end{remark*}
              \begin{prop}
                  The angle $\alpha_n$ is defined correctly and the following inequalities are true:
                  \begin{align*}
                      M_{n+1} &\leq \sqrt{\mu_n},\\
                      V_n &\leq \max(2\sqrt{\mu_n}, M_n),\\
                      U_n &\leq \sqrt{\mu_n}.
                  \end{align*}
                  With the values $U_n$, $V_n$, $\gamma_n$, $\alpha_n$ defined like this the following is true:
                  \begin{align*}
                      \langle u_n, v_n \rangle &= 0,\\
                      \langle u_n, v_{n+1} \rangle &= a_n/c_n,\\
                      \langle v_n, v_{n+1} \rangle &= 1/c_n.
                  \end{align*}
              \end{prop}
              \begin{proof}
                  Firstly $\alpha_n$ is defined correctly, since
                  $$
                  V_n V_{n+1} \geq V_n M_{n+1} \geq \frac{2}{\sqrt{\smash[b]{|c_n|}}} \frac{1}{\sqrt{\smash[b]{|c_n|}}}
                   = \frac{2}{|c_n|}
                  $$
                  which means that the absolute value of the arccosinus argument is always less than $1/2$. Now taking into
                  account that $|\cos{\alpha_n}|$ is less than or equal to $1/2$, we have that $|\cos{\gamma_n}| = |\sin{\alpha_n}|$ is always greater than $1/2$. It is the fact which will use later on in this proof.
                  
                  Trivially $M_{n+1} \leq \sqrt{\mu_n}$ and $V_n \leq \max(2\sqrt{\mu_n}, M_n)$. Next
                  $$
                      U_n = |U_n| \leq 2 \frac{|a_n|}{|c_n|} \frac{1}{V_{n+1}} \leq 2 \frac{\sqrt{|a_n|}}{\sqrt{|c_n|}} \leq \sqrt{\mu_n}.
                  $$
                  It is easy to notice that the angles and $U_n$ are chosen in such way that the scalar product conditions are 
                  satisfied.
                  Finally, we are able to lay out the vectors $v_n$, $u_n$ and $v_{n+1}$ with the prescribed angles 
                  since we have $\beta_n = \pi/2 = (\pi/2 \pm \alpha_n) \mp \alpha_n = \gamma_n \mp \alpha_n$,
                  where we choose the '$\mp$' sign accordingly to our choice in the expression of the $\gamma_n$ angle.
              \end{proof}
          \noindent\textbf{Case 3:} $\mu_n = (1 + |b_n|)/|d_n|$\\
              This case is almost identical to the previous one.\\
              Here we will have $u_n$ orthogonal to $v_{n+1}$.
              Assign:
              \begin{align*}
                  M_{n+1} &:= \max\biggl(\smash[t]{\frac{\sqrt{|b_n|}}{\sqrt{|d_n|}}}, \frac{1}{\sqrt{\smash[b]{|d_n|}}}\biggr),\\
                  V_n &:= \max\left(M_n, \frac{2}{\sqrt{\smash[b]{|d_n|}}}\right),\\
                  \alpha_n &:= \arccos{\frac{1}{-d_n V_n V_{n+1}}},\\
                  \beta_n &:= \frac{\pi}{2} \pm \alpha_n,\\
                  U_n &:= \frac{b_n}{d_n \cos{\beta_n} V_n}.
              \end{align*}
              \begin{remark*}
                  We choose plus or minus in the expression of $\beta_n$ in order to make the $b_n/(d_n \cos{\beta_n})$ always positive.
              \end{remark*}
              \begin{prop}
                  The angle $\alpha_n$ is defined correctly and the following inequalities are true:
                  \begin{align*}
                      M_{n+1} &\leq \sqrt{\mu_n},\\
                      V_n &\leq \max(2\sqrt{\mu_n}, M_n),\\
                      U_n &\leq \sqrt{\mu_n}.
                  \end{align*}
                  With the values $U_n$, $V_n$, $\beta_n$, $\alpha_n$ defined like this the following is true:
                  \begin{align*}
                      \langle u_n, v_n \rangle &= b_n/d_n,\\
                      \langle u_n, v_{n+1} \rangle &= 0,\\
                      \langle v_n, v_{n+1} \rangle &= -1/d_n.
                  \end{align*}
              \end{prop}
              \begin{proof}
                  Firstly $\alpha_n$ is defined correctly, since
                  $$
                  V_n V_{n+1} \geq V_n M_{n+1} \geq \frac{2}{\sqrt{\smash[b]{|d_n|}}} \frac{1}{\sqrt{\smash[b]{|d_n|}}}
                   = \frac{2}{|d_n|}
                  $$
                  which means that the absolute value of the arccosinus argument is always less than $1/2$. Now taking into
                  account that $|\cos{\alpha_n}|$ is less than or equal to $1/2$, we always have $|\cos{\beta_n}| > 1/2$.
                  
                  Trivially $M_{n+1} \leq \sqrt{\mu_n}$ and $V_n \leq \max(2\sqrt{\mu_n}, M_n)$. Next
                  $$
                      U_n = |U_n| \leq 2 \frac{|b_n|}{|d_n|} \frac{1}{V_n} \leq 2 \frac{\sqrt{|b_n|}}{\sqrt{|d_n|}} \leq \sqrt{\mu_n}.
                  $$
                  It is easy to notice that the angles and $U_n$ are chosen in such way that the scalar product conditions are 
                  satisfied.
                  Finally, we are able to lay out the vectors $v_n$, $u_n$ and $v_{n+1}$ with the prescribed angles 
                  since we have $\gamma_n = \pi/2 = (\pi/2 \pm \alpha_n) \mp \alpha_n = \beta_n \mp \alpha_n$,
                  where we choose the '$\mp$' sign accordingly to our choice in the expression of the $\beta_n$ angle.
              \end{proof}
          In each of three cases we guaranteed that $M_{n+1} \leq \sqrt{\mu_n}$ and
            that $V_n \leq \max(M_n, 2\sqrt{\mu_n})$.
          Hence we get that $V_n$ is bounded up to some constant by the $\max(\sqrt{\mu_{n-1}}, \sqrt{\mu_n})$. Due to all three propositions we also have an estimated bound for $U_n$: we always get
          $U_n \leq \sqrt{\mu_n}$. Thus the constructed vector lenghs sequences $V_n$ and $U_n$ belong to $l^2$.\\
          In the end let us choose such $v_1^*$ that $\langle v_1, v_1^*\rangle$ is equal to $-1$.
          It is possible since we earlier set $M_1 = 1$ which means that the vector $v_1$ is not trivial, because it has
            a length greater than zero.
          Additionally we set all the other $v^*_n$ and $u^*_n$ to zero in order to guarantee that for any $n > 1$ we have $\Xi_n$ equal to $1$.
          The trace of such operator is obviously equal to $-1$. The proposition is proven.
      \end{proof}
      The proof of the theorem is finished with the proof of the statements~\ref{inf-dim-statement} and~\ref{k-dim-statement}.
  \end{proof}
    
    
\medskip
% E-mail: aapyshkin@gmail.com
\bigskip
\begin {thebibliography}{20}
    \bibitem{azoff}
    E.~\!Azoff, H.~\!Shehada,
    \emph{Algebras generated by mutually orthogonal idempotent operators}.
    J. Oper. Theory, 29 (1993), 2, 249--267.
    \bibitem{bbb} 
    A. Baranov, Yu. Belov, A. Borichev,                                       
    \emph{Hereditary completeness for systems of exponentials and reproducing kernels},
    Adv. Math., 235 (2013), 1, 525--554.
    \bibitem{bbb1}
    A. Baranov, Yu. Belov, A. Borichev, 
    \emph{Spectral synthesis in de Branges spaces},
    Geom. Funct. Anal. (GAFA), 25 (2015), 2, 417--452.
    \bibitem{ad_preprint}
    A.D.~\!Baranov, D.V.~\!Yakubovich,
    \emph{Completeness and spectral synthesis of nonselfadjoint one-dimensional
    perturbations of selfadjoint operators}.
    arXiv:1212.5965 [math.FA]
    \bibitem{katavolos}
    A.~\!Katavolos, M.~\!Lambrou, M.~\!Papadakis,
    \emph{On some algebras diagonalized by $M$-bases of $\ell^2$}.
    Integr. Equat. Oper. Theory, 17 (1993), 1, 68--94.
    %\bibitem{wermer}
    %J.~\!Wermer,
    %\emph{On invariant subspaces of normal operators}.
    %Proc. Amer. Math. Soc., 3(1952), 2, 270--277.
    \bibitem{larson}
    D.~\!Larson, W.~\!Wogen,
    \emph{Reflexivity properties of $T\bigoplus0$}.
    J. Funct. Anal., 92 (1990), 448--467.
    %\bibitem{rotfeld}
    %В.В.~\!Пеллер,
    %\emph{Операторы Ганкеля и их приложения}.
    %Издательство РХД, Ижевск(2005).
    %N.K.~\!Nikol'skii,
    %\emph{Complete extensions of Volterra operators},
    %Izv. Akad. Nauk SSSR Ser. Mat 33(1969), 1349--1355. (Russian)

\end{thebibliography}
\vspace{1em}
\noindent{\bf Keywords:} complete minimal system, biorthogonal system, hereditary completeness, strong M-basis, summation method.

\end{document}
