\documentclass[12pt]{amsart}
\input{preamble}
\setlength{\emergencystretch}{2pt}
\newtheoremstyle{case}{}{}{}{}{}{:}{ }{}
\theoremstyle{case}
\newtheorem{case}{Case}

\begin{document}
\title{On $k$ point density problem for band-diagonal $M$-bases}
\author{Alexey Pyshkin}
\begin{abstract}
  In the early 1990s the works of Larson, Wogen and Argyros, Lambrou, Longstaff
    disclosed an example of a strong tridiagonal $M$-basis that was not rank one dense.
  Later Katavolos, Lambrou and Papadakis studied $k$ point density property of this example.
  In this paper we present new methods for the analysis of $k$ point density
    and rank one density properties for band-diagonal $M$-bases.
\end{abstract}
\keywords{biorthogonal system, $M$-basis, rank one density, two point density}
\thanks{The author was supported by RFBR (the project~16-01-00674) and by «Native towns», a social investment program of PJSC «Gazprom Neft».}
\maketitle

\section{Introduction}
  \subsection{Density properties}
    Consider the infinite-dimensional real Hilbert space $\cal{H}$.
    Suppose that $\cal{H}$ has an orthonormal basis $\{e_j\}_{j=0}^\infty$.
    The sequence $\fsys=\seq{f}$ is called \emph{minimal} if none of its elements can be approximated by the linear combinations of the others.
    The system $\fsys$ is complete and minimal when and only when it possesses a unique biorthogonal system $\fstarsys$.
    We call the minimal system $\fsys$ \emph{band-diagonal} if there exists $L \in \mathbb{N}$ such that $\inner{f_t}{e_l} = \inner{f^*_t}{e_l} = 0$
      whenever $\lvert t - l \rvert > L$.
    We say that $\fsys$ is an $M$-basis if $\fstarsys$ is complete as well.
    
    Consider the operator algebra $\cal{A} = \{T\in B(\cal{H}): Tf_n = \lambda_n f_n, \text{ for some } \lambda_n \in \mathbb{R}, n \geq 0\}$
      and the algebra $R_1(\cal{A})$ generated by rank one operators of $\cal{A}$.
    We are interested in the following properties of the algebra $\cal{A}$.
    %\begin{definition}[\mathit one point density property]
      %\label{1pd}
      %We say that $\fsys$ is \emph{one point dense} if for any $x \in \cal{H}$ and $\varepsilon > 0$
        %there exists such $T\in \cal{A}$ that $||Tx - x|| < \varepsilon$.
    %\end{definition}
    \begin{definition}[$k$ point density property]
      \label{kpd}
      We say that the algebra $\cal{A}$ is \emph{$k$ point dense} if for any $x_1, x_2,\dots x_k \in \cal{H}$ and $\varepsilon > 0$
        there exists such $T\in \cal{A}$ that $||Tx_s - x_s|| < \varepsilon$ for any $1 \leq s \leq k$.
    \end{definition}
    The definition for $k=1$ is equivalent to $\fsys$ being a \emph{strong $M$-basis} (see~\cite{katavolos}):
      the system $\fsys$ is called a \emph{strong $M$-basis} if for any $x\in\cal{H}$ we have $x \in \overline{span}\big(\inner{x}{f^*_n}f_n\big)$, where
      $\overline{span}$ denotes the closed linear span.
    \begin{definition}[rank one density property]
      \label{r1d}
      We say that the algebra $\cal{A}$ is \emph{rank one dense} if the unit ball of rank one subalgebra $R_1(\cal{A})$
        is dense in the unit ball of $\cal{A}$ in the strong operator topology.
    \end{definition}
    By abuse of notation, we say that $\fsys$ is $k$ point dense (rank one dense)
      when the corresponding algebra $\cal{A}$ is $k$ point dense (rank one dense).

    Notice that rank one density property implies $k$ point density property for any $k$.
    %Conversely, there is an easy compactness argument which shows that $\fsys$ is rank one dense if it is
    %  $k$ point dense for any $k > 0$.

  \subsection{Motivation}
    %It is well known that the last definition is equivalent to $R_1(\cal{A})$ being dense
      %in $\cal{A}$ in the ultraweak (or $\sigma$-weak) topology.
    %Rank one density property can be considered as a generalization of the notion of \emph{linear summation method} for the system $\fsys$.
    %We say that the system $\fsys$ admits a linear summation method if there exist $\alpha_{kn} \in \mathbb{C}, n \in \mathbb{N}, 0 < k < k_n$
      %such that for any $x \in \cal{H}$,
      %\[
        %\lim_{n \to \infty} \sum_k \alpha_{kn} \inner{x}{f^*_k}f_k = x.
      %\]
    %Clearly, the existence of the linear summation method implies rank one density property.

    %Notice that rank one density property~\eqref{r1d} implies two point density property~\eqref{kpd}, and~\eqref{kpd}
      %in its turn implies the one point density property~\eqref{1pd}.
    %But is it true that $\eqref{1pd}$ implies $\eqref{r1d}$ or that~\eqref{kpd} implies~\eqref{r1d}?

    %It is now a well-known fact that for a subspace lattice generated from an $M$-basis the complete distributivity of its lattice is equivalent to
      %the property~\eqref{1pd} (see~\cite{argyroslambrou} for a proof).
    %In the same paper the following question was raised: does the complete distributivity of $\lattice$ imply rank one density property?
    %The answer was already known to be positive in the case of a totally ordered lattice~\cite{erdos}, and
      %Longstaff proved it for a finite-dimensional Hilbert space in~\cite{longstaff}.
    %Later Laurie and Longstaff discovered that rank one density holds in the case of commutative subspace lattices~\cite{laurielongstaff}.
    Long\-staff in~\cite{longstaff} studied abstract subspace lattices and corresponding operator algebras.
    In that paper Longstaff raised an important question: does one point density property always imply rank one density property?

    The solution remained unknown until Larson and Wogen showed~\cite{larson} that the answer is negative.
    They constructed an example of a vector system $\fsys$ such that it is one point dense but does not possess rank one density property.
    \begin{example}[Larson--Wogen system $\fsys_{LW}$ parameterized with real $a_n$]
      \label{lw-sys}
      For any $j \geq 0$ we define
      \begin{align*}
        &f_{2j+1}=-a_{2j+1}e_{2j} + e_{2j+1} + a_{2j+2}e_{2j+2}, \qquad &f_{2j}=e_{2j},\\
        &f^*_{2j}=-a_{2j}e_{2j-1} + e_{2j} + a_{2j+1}e_{2j+1}, \qquad &f^*_{2j+1}=e_{2j+1},
      \end{align*}
      where $a_n$ are nonzero real numbers for any $n > 0$ and $a_0 = 0$.
    \end{example}
    The construction presented by Larson and Wogen was remarkably simple and elementary,~--- notice that the matrices corresponding to
      the vectors $\{f_j\}_{j=0}^\infty$ and $\{f^*_j\}_{j=0}^\infty$ are both tridiagonal.
    Afterwards this example was also studied in~\cite{argyroslambrou} (see Addendum), by Azoff and Shehada in~\cite{azoff}, in~\cite{me1}.
    In 1993 Katavolos, Lambrou and Papadakis in~\cite{katavolos} performed a deep analysis of the density properties
      of this vector system and deduced that for $\fsys_{LW}$ one point density does not imply rank one density.
    Moreover, they showed that for such system rank one density is equivalent to two point density.

    We are going to consider band-diagonal systems similar to the one regarded by Larson and Wogen and to determine the exact conditions
      for $k$ point density property of such vector systems.
    In this paper we present a few new techniques for analysis of $k$ point density and rank one density of band-diagonal vector systems.

    In the next section we will gather some basic facts and outline the main idea of the paper.
    In Section~\ref{section:lw-sys} we perform the analysis for Larson--Wogen example, providing the simpler proof of Theorems 2.1 and 2.2 in~\cite{katavolos}.
    In Section~\ref{section:pentadiagonal} we prove a similar theorem for one pentadiagonal system.
\section{Preliminaries}
  \label{sec:preliminaries}
  Suppose that $\fsys=\{f_n\}_{n=0}^\infty$ is an arbitrary band-diagonal $M$-basis and $\fstarsys = \{f^*_n\}_{n=0}^\infty$ is its biorthogonal sequence.
  In this section we establish several facts about $\fsys$.
  \begin{prop}
  %It means that $Tr(TR) = 0$ for each $R \in \cal{R}_1(\cal{A})$ which is equivalent to $\inner{Tf_n}{f_n^*} = 0$ for any $n$.
    The system $\fsys$ is rank one dense if and only if any trace class operator $T$,
      such that $\inner{Tf_n}{f_n^*} = 0$ for any $n \geq 0$, has  zero trace.
  \end{prop}
  \begin{proof}
    It is well known that rank one density property is equivalent to $R_1(\cal{A})$ being dense
      in $\cal{A}$ in the ultraweak (or $\sigma$-weak) topology (see~\cite{katavolos}, Theorem 2.2).
  \end{proof}
  \begin{prop}
    The system $\fsys$ is $k$ point dense if and only if any $k$-dimensional operator $T$,
      such that $\inner{Tf_n}{f_n^*} = 0$ for any $n \geq 0$, has  zero trace.
  \end{prop}
  \begin{proof}
    In the paper~\cite{katavolos} authors proved the proposition for $k = 2$.
    For greater $k$-s the same reasoning works.
  \end{proof}
  For an arbitrary linear operator $T$ we will be interested in the differences between
    the partial sums of the Fourier series using the system $\fsys$ and
    partial sums of the canonical Fourier series (using the orthonormal basis $\{e_n\}_{n=0}^\infty$):
  \begin{equation}
    \label{eq:xi}
    \Xi_n = \sum_{m=0}^n \inner{Tf_m}{f_m^*} - \sum_{m=0}^n \inner{Te_m}{e_m},
  \end{equation}
    where $\langle \cdot, \cdot\rangle$ denotes the scalar product in $\cal{H}$.
  It appears that $\Xi_n$ takes a concise and compact form for the finite-band system $\fsys$, and it is much easier to study $\Xi_n$
    than, for example, $\inner{Tf_m}{f_m^*}$.

  \begin{prop}
    \label{prop:reformulation}
    The operator $T$ is a trace class operator annihilating the subalgebra $R_1(\cal{A})$ if and only if
      for any $n \geq 0$ one has 
        \begin{equation}
          \label{eq:prop:ref}
          \Xi_n + \sum_{m=0}^n \inner{Te_m}{e_m} = 0.
        \end{equation}
  \end{prop}
    We will use this formulation in the following sections.

  \medskip
  Now consider the operator $T$ which has a finite rank.
  In that case we write $T$ as a finite sum $T = \sum_{s=1}^k y^s \otimes x^s$,
    where $x^s, y^s \in \cal{H}$.

  Let us define vectors $v_n$ and $u_n$ in $\mathbb{R}^k$ as follows:
  \begin{align*}
    v_n &= (x^1_n, x^2_n, \dots, x^k_n),\\
    u_n &= (y^1_n, y^2_n, \dots, y^k_n),
  \end{align*}
  where $x^s_n = \inner{x^s}{e_n}$.
  Since $\inner{Te_m}{e_l} = \inner{u_m}{v_l}$ for any $m$ and $l$, we can rewrite $\Xi_n$ in terms of
    the scalar products of $\{u_n\}_{n=0}^\infty$ and $\{v_n\}_{n=0}^\infty$.
  In turn it means that~\eqref{eq:prop:ref} can be rewritten in terms of the scalar products
    of $\{u_n\}_{n=0}^\infty$ and $\{v_n\}_{n=0}^\infty$.

  Hence, the existence of $T$ might be reduced to the existence of
    the vectors $u_n$, $v_n$ in $\mathbb{R}^k$ such that the sequences $\{\lvert u_n\rvert\}_{n=0}^\infty$,
    $\{\lvert v_n\rvert\}_{n=0}^\infty$ are both square summable and~\eqref{eq:prop:ref} is satisfied.
  Thus, instead of looking for $k$ vectors $x^s$ and $y^s$ in $\cal{H}$, we might look for an infinite sequence
    of $k$-dimensional vectors $v_n$ and $u_n$ such that $\{v_n \}_{n=0}^\infty$, $\{u_n\}_{n=0}^\infty$ belong to $\ell^2(\mathbb{R}^k)$.
  That is one of the key ideas in our method of analysing $k$ point density property for $\fsys$.

  Thus, we have just found the following reformulation for $k$ point density property.
  \begin{prop}
    \label{prop:kreformulation}
    The following two statements are equivalent:
    \begin{enumerate}
      \item there exists a $k$-dimensional operator $T$ which annihilates $R_1(\cal{A})$
        such that $Tr\, T \neq 0$,
      \item there exist vectors $\{u_n\}_{n=0}^\infty$, $\{v_n\}_{n=0}^\infty$ in $\ell^2(\mathbb{R}^k)$ such that
        for the operator $T = \displaystyle\sum_{t,l=0}^\infty \inner{u_t}{v_l} e_t \otimes e_l$ we have
        \begin{equation}
          \label{eq:thm}
          \Xi_n + \sum_{m=0}^n \inner{Te_m}{e_m} = 0
        \end{equation}
          for any $n \geq 0$.
    \end{enumerate}
  \end{prop}
  As we already mentioned, the equation~\eqref{eq:thm} can be expressed via $u_n$ and $v_n$.
  Moreover, we can also write the trace of $T$ in terms of $u_n$, $v_n$:
  %\begin{prop*}
    \begin{equation}
      \label{eq:propstar}
      %\begin{align*}
        Tr\,T = \sum_{s=1}^k \langle y^s, x^s \rangle = \sum_{s=1}^k \sum_{n=0}^\infty y^s_n x^s_n
              = \sum_{n=0}^\infty \sum_{s=1}^k y^s_n x^s_n = \sum_{n=0}^\infty \langle u_n, v_n \rangle.
      %\end{align*}
    \end{equation}
  %\end{prop*}
  Essentially, $k$ point density property can be viewed as a
    possibility of laying out the sequence of vectors in $\mathbb{R}^k$ which are constrained with
    a series of relations~\eqref{eq:thm} and~\eqref{eq:propstar}.
\input{lw-classification}
\input{pentadiagonal-classification}
\bigskip

\section{Acknowledgements}
  %This is part of author's Ph.D. thesis, written under the supervision of Anton Baranov at the PDMI RAS.
  The author gratefully acknowledges the many helpful suggestions of Anton Baranov during the preparation of the paper.

\input{bib}
\end{document}
